### 2017-02-03 Paper_v1.tex
Feb3

To better understand which parameters and parameter combinations influenced the performance of the kinetic model, we performed sensitivity analysis (Fig.~\ref{fig:Sensitivity}).
We perturbed each $V^{max}$ parameter, either individually or in pairwise combinations and measured the change in either CAT production or the overall system state.
CAT production was most sensitive to the CAT synthesis reaction, oxidative phosphorylation, and the pyruvate-consuming alanine synthesis reaction (Fig.~\ref{fig:Sensitivity}, top, section A).
%Taking into account these three reactions, and the next 16 most important reactions (section B), we saw a common theme of reactions involving the cofactors ATP, NADH, NADPH, and coenzyme A, as well as the metabolites pyruvate and glutamate.
We saw a common theme of the most important reactions producing or consuming the cofactors ATP, NADH, NADPH, and coenzyme A, as well as the metabolites pyruvate and glutamate.
Of the 25 reactions to which CAT production was most sensitive, 9 produced or consumed ATP, making it the most represented in these top reactions (with the exception of hydrogen and phosphate ion).
The next most represented were pyruvate, glutamate, and ADP with 7 reactions each, followed by coenzyme A, $\alpha$-ketoglutarate, NAD/NADH, and NADP/NADPH, with 6 reactions each.
This makes sense, as glutamate was an important precursor for the synthesis of other amino acids required by CAT production.
Meanwhile, the cofactors provided energy to power CAT synthesis, while pyruvate was important for energy generation following glucose depletion.
In addition, pyruvate was required for the synthesis of several amino acids.
The pairwise sensitivities (off-diagonal elements) were different from the corresponding first-order sensitivities (diagonal elements), and led to interesting outcomes.
The combination of certain reactions had a much greater or lesser effect on CAT production than that of the individual reactions by themselves.
For example, glutamine synthesis and arginine degradation were both among the most important reactions to CAT production (they ranked 5th and 10th, respectively).
This was likely because they both affected the sensitive glutamine-glutamate balance; glutamine synthesis consumes glutamate, while arginine degradation produces it.
However, when both were perturbed, their combined effect on the model was low, as the respective contributions to consumption and production of glutamate cancelled.
An example of positive synergy can be seen in cometabolite interconversion.
Pyridine nucleotide transhydrogenase catalyzes two reactions: one converts NAD and NADPH into NADH and NADP, while the other does the reverse and also generates a proton gradient.
Increasing one or the other has little effect on the model, as the reaction is hampered by the loss of reactants.
Increasing both, however, allows all cometabolites to be conserved and the reactions to continue unhindered.
Thus, the pairwise sensitivity is much higher than the sum of the first-order sensitivities.

@@

Gene knockouts in the electron transport chain significantly reduced the performance of the CFPS reaction (Fig.~\ref{fig:oxKO_ssFBA_yields}).
A key finding of both the CAT and overall system state sensitivity analysis was the importance of oxidative phosphorylation.
To investigate this further, we knocked out key oxidative phosphorylation reactions in the ensemble of kinetic models to examine the effect on glucose uptake and CAT production.
%A single \textit{cyd} knockout reduced the CAT carbon yield from 7.9\% to 2.6\% (Table~\ref{tbl:yield_breakdown}).
A single \textit{cyd} knockout reduced the CAT carbon yield from 2.7\% to 0.9\% (Table~\ref{tbl:yield_breakdown}).
%In addition, the glucose uptake rate was reduced compared to that of the control (no knockouts).
%On the other hand, a \textit{nuo} knockout showed a less dramatic decrease in yield,
%reducing the CAT carbon yield to 6.9\%; however, the glucose uptake rate remained similar to that of the control.
On the other hand, a \textit{nuo} knockout showed a less dramatic decrease in yield,
reducing the CAT carbon yield to 2.3\%.
%; however, the glucose uptake rate remained similar to that of the control.
%Knocking out \textit{app} increased CAT yield to 8.3\%, but this increase was not statistically significantly different from that of the control.
Knocking out \textit{app} did not change the CAT yield (it remained at 2.7\%).
%Lastly, knocking out all three reactions reduced the CAT yield to 3.0\%, but this was not statistically significantly different from the \textit{cyd} knockout alone.
Lastly, knocking out all three reactions reduced the CAT yield to 0.7\%, similar to knocking out the \textit{cyd} alone.
Thus, the model suggested the key step in oxidative phosphorylation was catalyzed by the gene product of \textit{cyd}.
However, while disruption of \textit{cyd} significantly reduced the CAT carbon yield, it did not eliminate the ability of CFPS reaction to produce CAT.
This suggested there was a mixture of energy sources supporting CAT production, with the most significant being oxidative phosphorylation.
%The \textit{cyd} enzyme is responsible for transferring electrons with oxygen as an electron acceptor allowing the release of energy to form ATP.
%The sensitivity analysis showed oxidative phosphorylation was significant for CAT production as well as the system state.

@@

We chose this time window (during the first phase of CAT production) because it was approximately linear in both glucose consumption and by-/production formation.
The ssFBA calculation had no adjustable parameters; bounds on transcription and translation rates, and biochemical fluxes were either estimated from data, or
from mechanistic models parameterized from literature.

@@

The ensemble of ssFBA simulations predicted CAT formation as a function of time during the first hour of production when constrained by the experimental metabolite data (Fig.~\ref{fig:oxKO_ssFBA_yields}A).

@@

(iii) metabolite fluxes constrained by the CAT data, and realistic transcriptional/translational constraints and knockouts of amino acid synthesis reactions of amino acids supplemented in the \textit{E. coli} extract preparation (Fig.~\ref{fig:oxKO_ssFBA_yields}B).
The physiological theoretical maximum CAT carbon yield (case i) was 21.8\% $\pm$ 2.8\% (Fig.~\ref{fig:oxKO_ssFBA_yields}B, left); this represents optimal network performance if glucose, oxygen and amino acids were produced or consumed at their upper bounds, with bounded transcription and translation rates (96\% without glucose contribution in the carbon yield calculation).
For case ii, the optimal CAT carbon yield decreased to 18.2\% $\pm$ 3.0\% (Fig.~\ref{fig:oxKO_ssFBA_yields}B, middle).
Lastly, when metabolite constraints were applied with experimental measurements of measurements (case iii), the predicted carbon yield was 6.0\% $\pm$ 2.0\%.
By comparison, the best-fit parameter set for the kinetic model predicted a CAT carbon yield (without arginine and glutamate) of 7.9\%, equivalent to 36\% of the optimal case (i).

@@

A similar distribution of the carbon contribution to CAT yield was seen across the best-fit set and all knockouts (Table~\ref{tbl:yield_breakdown}).
In all cases, glutamate was responsible for about two-thirds of carbon consumption toward CAT.
This was due to its role in generating other amino acids and as a possible energy source for metabolism.
The much greater consumption of this one amino acid was made possible by its much larger initial condition, as it was present in the cell media in the form of magnesium glutamate, ammonium glutamate, and potassium glutamate.
% [CITE? THESIS NOT CURRENTLY IN BIBLIOGRAPHY].
Glucose made the next largest contribution, between 20\% and 30\%, dwarfing all amino acids other than glutamate.
This makes sense, as glucose powers the entire metabolism during the first hour, including energy species synthesis and amino acid synthesis.
%We also investigated the energy efficiency of CAT production across the kinetic models and experimental dataset.
%The best-fit set, $\Delta$app, and experimental data had energy efficiencies of 2.6\%, $\Delta$nuo had an efficiency of 2.2\%, and $\Delta$cyd and $\Delta$cyd$\Delta$nuo$\Delta$app had efficiencies of 0.8\%.
%The best-fit set, $\Delta$app, and experimental data had energy efficiencies of 2.6\%, calculated as a ratio of CAT production to glucose consumption, each converted into an equivalent number of ATP molecules.
%$\Delta$nuo had an efficiency of 2.2\%, and $\Delta$cyd and $\Delta$cyd$\Delta$nuo$\Delta$app had efficiencies of 0.8\%.
%The energy efficiencies across the different cases were more or less proportional to the carbon yields, and in turn the total amount of CAT synthesis.
Taken together, these results show that oxidative phosphorylation, particularly \textit{cyd}, is important to efficient CAT production.

Furthermore, we performed a carbon balance on the best-fit set to determine the proportion of carbon consumption going toward CAT synthesis (Fig.~\ref{fig:Carbon_Balance}).
%To better understand where carbon flux goes besides toward CAT, we examined the proportion of amino acid consumption that was due to CAT synthesis in the best-fit set (Table~\ref{tbl:AA_breakdown}).
%Eight of the 20 amino acids had a flux-toward-CAT percentage of 100\% or higher.
%For six of these (isoleucine, leucine, methionine, phenylalanine, tryptophan, valine), synthesis was inactive or negligible, meaning that CAT synthesis was the only reaction that consumed these species.
%This is why methionine, and to a lesser extent isoleucine, leucine, and valine do not fit the experimental data as well as some other amino acids; consumption via CAT synthesis was not enough to fit the data, and no other reactions exist in the network to consume these species.
%For histidine and tyrosine, synthesis was active, allowing the percentage to be higher than 100\%.
%Another ten amino acids registered percentages lower than 100\%, meaning that they were consumed by other pathways in the network.
%The most extreme of these is glutamate, with a percentage of 0.2\%, because it was consumed by numerous reactions for the synthesis of other amino acids and as an energy substrate.
%Likewise, arginine, asparagine, glycine, and proline are consumed in the production of other amino acids, while cysteine and lysine are consumed to form other metabolites.
%ARG R_arg_deg1-4 go to GLU
%ASN R_asn_deg goes to ASP
%ASP R_thr, maybe negligible
%CYS cys_deg goes to pyr
%GLY R_gar goes to GLU
%LYS lys_deg goes to cadav
%PRO pro_deg goes to GLU
%SER R_glyA, maybe negligible
%THR R_thr_deg4, maybe negligible
%Finally, alanine and glutamine increased during the timecourse, meaning that synthesis outweighed all consumption (including consumption toward CAT).

@@

\begin{table}
\centering
    \caption{CAT carbon yield breakdown for best-fit set, knockouts, and experimental data. Carbon produced as CAT, carbon consumed as glucose and each amino acid, sum of consumed species, and yield.}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{lrrrrrr} \toprule
        Carbon Produced (C-mM) & Best-fit & $\Delta$cyd & $\Delta$nuo & $\Delta$app & \parbox{1 cm}{$\Delta$cyd $\Delta$nuo $\Delta$app} & Data \\ \hline
        CAT & 20.9 & 6.5 & 18.1 & 21.4 & 5.1 & 21.6 \\ \midrule
        Carbon Consumed (C-mM) \\ \hline
        GLC & 215.4 & 215.4 & 215.4 & 215.4 & 159.8 & 215.4 \\ \hline
        ALA & 0.0 & 0.0 & 1.7 & 0.0 & 0.0 & 0.0 \\ \hline
%        ARG & 10.2 & 0.9 & 1.1 & 9.9 & 1.3 & - \\ \hline
        ASN & 6.2 & 6.3 & 6.2 & 6.2 & 6.3 & 6.3 \\ \hline
        ASP & 7.5 & 0.0 & 3.9 & 7.5 & 0.0 & 9.6 \\ \hline
        CYS & 3.0 & 2.9 & 3.0 & 3.1 & 2.9 & 3.7 \\ \hline
        GLN & 0.0 & 1.8 & 0.0 & 0.0 & 2.7 & 0.0 \\ \hline
%        GLU & 492.6 & 505.1 & 528.2 & 505.6 & 501.8 & - \\ \hline
        GLY & 3.1 & 1.1 & 2.6 & 3.1 & 0.9 & 1.5 \\ \hline
        HIS & 0.2 & 0.4 & 1.1 & 0.2 & 0.3 & 0.0 \\ \hline
        ILE & 1.0 & 0.3 & 0.8 & 1.0 & 0.2 & 1.7 \\ \hline
        LEU & 1.4 & 0.4 & 1.2 & 1.4 & 0.3 & 2 \\ \hline
        LYS & 10.7 & 13.2 & 13.1 & 10.7 & 13.2 & 8.3 \\ \hline
        MET & 0.8 & 0.2 & 0.7 & 0.8 & 0.2 & 2.9 \\ \hline
        PHE & 3.2 & 1.0 & 2.8 & 3.3 & 0.8 & 1.6 \\ \hline
        PRO & 2.4 & 0.2 & 0.7 & 2.4 & 0.2 & 1.9 \\ \hline
        SER & 2.5 & 2.1 & 2.4 & 2.5 & 2.1 & 1.8 \\ \hline
        THR & 3.4 & 2.9 & 3.3 & 3.4 & 2.8 & 2.8 \\ \hline
        TRP & 1.0 & 0.3 & 0.8 & 1.0 & 0.2 & 1.2 \\ \hline
        TYR & 1.1 & 0.4 & 1.1 & 1.1 & 0.4 & 0.6 \\ \hline
        VAL & 1.4 & 0.4 & 1.2 & 1.5 & 0.4 & 2.4 \\ \midrule
%        Sum & 767.1 & 755.3 & 791.3 & 780.1 & 696.8 & - \\ \hline
        Sum & 264.3 & 249.3 & 262.0 & 264.6 & 193.7 & 263.7 \\ \midrule
%        Yield & 2.7\% & 0.9\% & 2.3\% & 2.7\% & 0.7\% & - \\ \hline
        Yield & 7.9\% & 2.6\% & 6.9\% & 8.1\% & 2.7\% & 8.2\% \\ \bottomrule
    \end{tabular}
\label{tbl:yield_breakdown}
\end{table}

>>>>

To better understand which parameters and parameter combinations influenced the performance of the kinetic model, we performed sensitivity analysis (Fig.~\ref{fig:Sensitivity}).
We perturbed each $V^{max}$ parameter, either individually or in pairwise combinations and measured the change in either CAT production or the overall system state.
CAT production was most sensitive to the CAT synthesis reaction, oxidative phosphorylation, and the pyruvate-consuming alanine synthesis reaction (Fig.~\ref{fig:Sensitivity}, top, section A).
%Taking into account these three reactions, and the next 16 most important reactions (section B), we saw a common theme of reactions involving the cofactors ATP, NADH, NADPH, and coenzyme A, as well as the metabolites pyruvate and glutamate.
We saw a common theme of the most important reactions producing or consuming the cofactors ATP, NADH, NADPH, and coenzyme A, as well as the metabolites pyruvate and glutamate.
Of the 25 reactions to which CAT production was most sensitive, 9 produced or consumed ATP, making it the most represented in these top reactions (with the exception of hydrogen and phosphate ion).
The next most represented were pyruvate, glutamate, and ADP with 7 reactions each, followed by coenzyme A, $\alpha$-ketoglutarate, NAD/NADH, and NADP/NADPH, with 6 reactions each.
This makes sense, as glutamate was an important precursor for the synthesis of other amino acids required by CAT production.
Meanwhile, the cofactors provided energy to power CAT synthesis, while pyruvate was important for energy generation following glucose depletion.
In addition, pyruvate was required for the synthesis of several amino acids.
The pairwise sensitivities (off-diagonal elements) were different from the corresponding first-order sensitivities (diagonal elements), and led to interesting outcomes.
The combination of certain reactions had a much greater or lesser effect on CAT production than that of the individual reactions by themselves.
For example, glutamine synthesis and arginine degradation were both among the most important reactions to CAT production (they ranked 5th and 10th, respectively).
This was likely because they both affected the sensitive glutamine-glutamate balance; glutamine synthesis consumes glutamate, while arginine degradation produces it.
However, when both were perturbed, their combined effect on the model was low, as the respective contributions to consumption and production of glutamate cancelled.
An example of positive synergy can be seen in cometabolite interconversion.
Pyridine nucleotide transhydrogenase catalyzes two reactions: one converts NAD and NADPH into NADH and NADP, while the other does the reverse and also generates a proton gradient.
Increasing one or the other has little effect on the model, as any increase in reaction flux is hampered by the imbalance created.
Increasing both, however, allows all cometabolites to balance, so that the reaction fluxes increase unhindered.
Thus, the pairwise sensitivity is much higher than the sum of the first-order sensitivities.

@@

To understand whether the CFPS performance was optimal, we calculated the carbon yield and energy efficiency of CAT production (Fig.~\ref{fig:?????}).
The best-fit parameter set for the kinetic model predicted a CAT carbon yield of 7.9\%, while the experimental dataset had a CAT carbon yield of 8.2\%.
This was calculated as the increase in CAT concentration times the CAT carbon number, divided by the sum of the consumption terms for glucose and all amino acids excpet arginine and glutamate, as no data were available for these, weighted by their respective carbon numbers.
To explain where the remainder of carbon was going, we performed a carbon balance for the best-fit set.
Of the other 92\% of carbon, 35\% accumulated as organic acids (lactate, acetate, succinate and malate) and 9\% accumulated as amino acids (alanine and glutamine).
The remaining 48\% went to the net accumulation of all other metabolites, particularly carbon dioxide.
The best-fit set produced CAT with an energy efficiency of 6.4\%.
This was calculated as the increase in CAT concentration times the CAT number of equivalent ATP molecules, divided by glucose consumption times times the number of equivalent ATP molecules for glucose, equal to 15 in the optimal case.
An additional 62\% of energy went to the accumulation of glycolysis metabolites, 6.4\% to TCA cycle metabolites, 0.2\% to pentose phosphate metabolites, and 25\% to acetate and lactate.
This shows that there is much room for improvement of the efficiency of CFPS.
Gene knockouts in the electron transport chain further reduced the performance of the CFPS reaction (Fig.~\ref{fig:oxKO_ssFBA_yields}).
A key finding of both the CAT and overall system state sensitivity analysis was the importance of oxidative phosphorylation.
To investigate this further, we knocked out key oxidative phosphorylation reactions in the ensemble of kinetic models to examine the effect on CAT production and carbon yield.
A single \textit{cyd} knockout reduced the CAT carbon yield from 7.9\% to 2.6\% (Table~\ref{tbl:yield_breakdown}).
On the other hand, a \textit{nuo} knockout showed a less dramatic decrease in yield,
reducing the CAT carbon yield to 6.9\%.
Knocking out \textit{app} increased CAT yield to 8.1\%, but this increase was not statistically significantly different from that of the control.
Lastly, knocking out all three reactions reduced the CAT yield to 0.7\%, similar to knocking out the \textit{cyd} alone.
Thus, the model suggested the key step in oxidative phosphorylation was catalyzed by the gene product of \textit{cyd}.
However, while disruption of \textit{cyd} significantly reduced the CAT carbon yield, it did not completely eliminate the production of CAT.
This suggested there was a mixture of energy sources supporting CAT production, with the most significant being oxidative phosphorylation.
%The \textit{cyd} enzyme is responsible for transferring electrons with oxygen as an electron acceptor allowing the release of energy to form ATP.

@@

We chose this time window (during the first phase of CAT production) because it was approximately linear both in glucose consumption and in the accumulation of most organic acids.
As the ssFBA calculation had no adjustable parameters, bounds on transcription and translation rates and biochemical fluxes were either estimated from data or from mechanistic models parameterized from literature.

@@

The ensemble of ssFBA simulations predicted CAT formation as a function of time during the first hour of production when constrained by the experimental metabolite data (Fig.~\ref{fig:oxKO_ssFBA_yields}C).

@@

(iii) metabolite fluxes constrained by the CAT data, and realistic transcriptional/translational constraints and knockouts of amino acid synthesis reactions of amino acids supplemented in the \textit{E. coli} extract preparation (Fig.~\ref{fig:oxKO_ssFBA_yields}D).
The physiological theoretical maximum CAT carbon yield (case i) was 21.8\% $\pm$ 2.8\% (Fig.~\ref{fig:oxKO_ssFBA_yields}D, left); this represents optimal network performance if glucose, oxygen and amino acids were produced or consumed at their upper bounds, with bounded transcription and translation rates (96\% without glucose contribution in the carbon yield calculation).
For case ii, the optimal CAT carbon yield decreased to 18.2\% $\pm$ 3.0\% (Fig.~\ref{fig:oxKO_ssFBA_yields}D, middle).
Lastly, when metabolite constraints were applied with experimental measurements of measurements (case iii), the predicted carbon yield was 6.0\% $\pm$ 2.0\% (Fig.~\ref{fig:oxKO_ssFBA_yields}D, right).
%By comparison, the best-fit parameter set for the kinetic model predicted a CAT carbon yield (without arginine and glutamate) of 7.9\%, equivalent to 36\% of the optimal case (i).
By comparison, the best-fit parameter set for the kinetic model predicted a CAT carbon yield of 7.9\%, equivalent to 36\% of the optimal case (i).

@@

%A similar distribution of the carbon contribution to CAT yield was seen across the best-fit set and all knockouts (Table~\ref{tbl:yield_breakdown}).
%In all cases, glutamate was responsible for about two-thirds of carbon consumption toward CAT.
%This was due to its role in generating other amino acids and as a possible energy source for metabolism.
%The much greater consumption of this one amino acid was made possible by its much larger initial condition, as it was present in the cell media in the form of magnesium glutamate, ammonium glutamate, and potassium glutamate.
%% [CITE? THESIS NOT CURRENTLY IN BIBLIOGRAPHY].
%Glucose made the next largest contribution, between 20\% and 30\%, dwarfing all amino acids other than glutamate.
%This makes sense, as glucose powers the entire metabolism during the first hour, including energy species synthesis and amino acid synthesis.
%We also investigated the energy efficiency of CAT production across the kinetic models and experimental dataset.
%The best-fit set, $\Delta$app, and experimental data had energy efficiencies of 2.6\%, $\Delta$nuo had an efficiency of 2.2\%, and $\Delta$cyd and $\Delta$cyd$\Delta$nuo$\Delta$app had efficiencies of 0.8\%.
%The best-fit set, $\Delta$app, and experimental data had energy efficiencies of 2.6\%, calculated as a ratio of CAT production to glucose consumption, each converted into an equivalent number of ATP molecules.
%$\Delta$nuo had an efficiency of 2.2\%, and $\Delta$cyd and $\Delta$cyd$\Delta$nuo$\Delta$app had efficiencies of 0.8\%.
%The energy efficiencies across the different cases were more or less proportional to the carbon yields, and in turn the total amount of CAT synthesis.
%Taken together, these results show that oxidative phosphorylation, particularly \textit{cyd}, is important to efficient CAT production.

Furthermore, we performed a carbon balance on the best-fit set to determine the proportion of carbon consumption going toward CAT synthesis (Fig.~\ref{fig:Carbon_Balance}).

%To better understand where carbon flux goes besides toward CAT, we examined the proportion of amino acid consumption that was due to CAT synthesis in the best-fit set (Table~\ref{tbl:AA_breakdown}).
%Eight of the 20 amino acids had a flux-toward-CAT percentage of 100\% or higher.
%For six of these (isoleucine, leucine, methionine, phenylalanine, tryptophan, valine), synthesis was inactive or negligible, meaning that CAT synthesis was the only reaction that consumed these species.
%This is why methionine, and to a lesser extent isoleucine, leucine, and valine do not fit the experimental data as well as some other amino acids; consumption via CAT synthesis was not enough to fit the data, and no other reactions exist in the network to consume these species.
%For histidine and tyrosine, synthesis was active, allowing the percentage to be higher than 100\%.
%Another ten amino acids registered percentages lower than 100\%, meaning that they were consumed by other pathways in the network.
%The most extreme of these is glutamate, with a percentage of 0.2\%, because it was consumed by numerous reactions for the synthesis of other amino acids and as an energy substrate.
%Likewise, arginine, asparagine, glycine, and proline are consumed in the production of other amino acids, while cysteine and lysine are consumed to form other metabolites.
%ARG R_arg_deg1-4 go to GLU
%ASN R_asn_deg goes to ASP
%ASP R_thr, maybe negligible
%CYS cys_deg goes to pyr
%GLY R_gar goes to GLU
%LYS lys_deg goes to cadav
%PRO pro_deg goes to GLU
%SER R_glyA, maybe negligible
%THR R_thr_deg4, maybe negligible
%Finally, alanine and glutamine increased during the timecourse, meaning that synthesis outweighed all consumption (including consumption toward CAT).

@@

\begin{table}
\centering
    \caption{CAT carbon yield breakdown for best-fit set, knockouts, and experimental data. Carbon produced as CAT, carbon consumed as glucose and each amino acid, sum of consumed species, and yield.}
    \renewcommand{\arraystretch}{1.3}
    \begin{tabular}{lrrrrrr} \toprule
        Carbon Produced (C-mM) & Best-fit & $\Delta$app & $\Delta$nuo & $\Delta$cyd & \parbox{1 cm}{$\Delta$app $\Delta$nuo $\Delta$cyd} & Data \\ \hline
        CAT & 20.9 & 21.4 & 18.1 & 6.5 & 5.1 & 21.6 \\ \midrule
        Carbon Consumed (C-mM) \\ \hline
        GLC & 215.4 & 215.4 & 215.4 & 215.4 & 159.8 & 215.4 \\ \hline
        ALA & 0.0 & 0.0 & 1.7 & 0.0 & 0.0 & 0.0 \\ \hline
%        ARG & 10.2 & 9.9 & 1.1 & 0.9 & 1.3 & - \\ \hline
        ASN & 6.2 & 6.2 & 6.2 & 6.3 & 6.3 & 6.3 \\ \hline
        ASP & 7.5 & 7.5 & 3.9 & 0.0 & 0.0 & 9.6 \\ \hline
        CYS & 3.0 & 3.1 & 3.0 & 2.9 & 2.9 & 3.7 \\ \hline
        GLN & 0.0 & 0.0 & 0.0 & 1.8 & 2.7 & 0.0 \\ \hline
%        GLU & 492.6 & 505.6 & 528.2 & 505.1 & 501.8 & - \\ \hline
        GLY & 3.1 & 3.1 & 2.6 & 1.1 & 0.9 & 1.5 \\ \hline
        HIS & 0.2 & 0.2 & 1.1 & 0.4 & 0.3 & 0.0 \\ \hline
        ILE & 1.0 & 1.0 & 0.8 & 0.3 & 0.2 & 1.7 \\ \hline
        LEU & 1.4 & 1.4 & 1.2 & 0.4 & 0.3 & 2.0 \\ \hline
        LYS & 10.7 & 10.7 & 13.1 & 13.2 & 13.2 & 8.3 \\ \hline
        MET & 0.8 & 0.8 & 0.7 & 0.2 & 0.2 & 2.9 \\ \hline
        PHE & 3.2 & 3.3 & 2.8 & 1.0 & 0.8 & 1.6 \\ \hline
        PRO & 2.4 & 2.4 & 0.7 & 0.2 & 0.2 & 1.9 \\ \hline
        SER & 2.5 & 2.5 & 2.4 & 2.1 & 2.1 & 1.8 \\ \hline
        THR & 3.4 & 3.4 & 3.3 & 2.9 & 2.8 & 2.8 \\ \hline
        TRP & 1.0 & 1.0 & 0.8 & 0.3 & 0.2 & 1.2 \\ \hline
        TYR & 1.1 & 1.1 & 1.1 & 0.4 & 0.4 & 0.6 \\ \hline
        VAL & 1.4 & 1.5 & 1.2 & 0.4 & 0.4 & 2.4 \\ \midrule
%        Sum & 767.1 & 780.1 & 791.3 & 755.3 & 696.8 & - \\ \hline
        Sum & 264.3 & 264.6 & 262.0 & 249.3 & 193.7 & 263.7 \\ \midrule
%        Yield & 2.7\% & 2.7\% & 2.3\% & 0.9\% & 0.7\% & - \\ \hline
        Yield & 7.9\% & 8.1\% & 6.9\% & 2.6\% & 2.7\% & 8.2\% \\ \bottomrule
    \end{tabular}
\label{tbl:yield_breakdown}
\end{table}
